\tool{}: Specification- and Syntax-based Automated Testing Linguistic Capabilities of NLP Models

### 2023-01-17 paper/fse23/tables/test-results-all-numbers.tex
modify table

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

\DefMacro{test-results-bl-lc7-num-tcs}{8,528}

@@

\DefMacro{test-results-bl-model0-lc7-num-fail}{3,741}
\DefMacro{test-results-bl-model0-lc7-num-failrate}{43.87}

@@

\DefMacro{test-results-bl-lc3-num-tcs}{6,786}

@@

\DefMacro{test-results-bl-model0-lc3-num-fail}{799}
\DefMacro{test-results-bl-model0-lc3-num-failrate}{11.77}

@@

\DefMacro{test-results-bl-lc4-num-tcs}{2,496}

@@

\DefMacro{test-results-bl-model0-lc4-num-fail}{2,427}
\DefMacro{test-results-bl-model0-lc4-num-failrate}{97.24}

@@

\DefMacro{test-results-bl-lc6-num-tcs}{1,000}

@@

\DefMacro{test-results-bl-model0-lc6-num-fail}{860}
\DefMacro{test-results-bl-model0-lc6-num-failrate}{86.00}

@@

\DefMacro{test-results-bl-lc5-num-tcs}{2,124}

@@

\DefMacro{test-results-bl-model0-lc5-num-fail}{1,871}
\DefMacro{test-results-bl-model0-lc5-num-failrate}{88.09}

@@

\DefMacro{test-results-bl-lc9-num-tcs}{7,644}

@@

\DefMacro{test-results-bl-model0-lc9-num-fail}{4,056}
\DefMacro{test-results-bl-model0-lc9-num-failrate}{53.06}

@@

\DefMacro{test-results-bl-lc2-num-tcs}{8,000}

@@

\DefMacro{test-results-bl-model0-lc2-num-fail}{1,680}
\DefMacro{test-results-bl-model0-lc2-num-failrate}{21.00}

@@

\DefMacro{test-results-bl-lc0-num-tcs}{1,716}

@@

\DefMacro{test-results-bl-model0-lc0-num-fail}{1,330}
\DefMacro{test-results-bl-model0-lc0-num-failrate}{77.51}

@@

\DefMacro{test-results-bl-lc1-num-tcs}{8,658}

@@

\DefMacro{test-results-bl-model0-lc1-num-fail}{26}
\DefMacro{test-results-bl-model0-lc1-num-failrate}{0.30}

@@

\DefMacro{test-results-bl-lc8-num-tcs}{7,644}

@@

\DefMacro{test-results-bl-model0-lc8-num-fail}{253}
\DefMacro{test-results-bl-model0-lc8-num-failrate}{3.31}

@@

\DefMacro{test-results-bl-model1-lc7-num-fail}{2,692}
\DefMacro{test-results-bl-model1-lc7-num-failrate}{31.57}

@@

\DefMacro{test-results-bl-model1-lc3-num-fail}{218}
\DefMacro{test-results-bl-model1-lc3-num-failrate}{3.21}

@@

\DefMacro{test-results-bl-model1-lc4-num-fail}{2,304}
\DefMacro{test-results-bl-model1-lc4-num-failrate}{92.31}

@@

\DefMacro{test-results-bl-model1-lc6-num-fail}{416}
\DefMacro{test-results-bl-model1-lc6-num-failrate}{41.60}

@@

\DefMacro{test-results-bl-model1-lc5-num-fail}{445}
\DefMacro{test-results-bl-model1-lc5-num-failrate}{20.95}

@@

\DefMacro{test-results-bl-model1-lc9-num-fail}{4,576}
\DefMacro{test-results-bl-model1-lc9-num-failrate}{59.86}

@@

\DefMacro{test-results-bl-model1-lc2-num-fail}{829}
\DefMacro{test-results-bl-model1-lc2-num-failrate}{10.36}

@@

\DefMacro{test-results-bl-model1-lc0-num-fail}{1,391}
\DefMacro{test-results-bl-model1-lc0-num-failrate}{81.06}

@@

\DefMacro{test-results-bl-model1-lc1-num-fail}{139}
\DefMacro{test-results-bl-model1-lc1-num-failrate}{1.61}

@@

\DefMacro{test-results-bl-model1-lc8-num-fail}{32}
\DefMacro{test-results-bl-model1-lc8-num-failrate}{0.42}

@@

\DefMacro{test-results-bl-model2-lc7-num-fail}{3,535}
\DefMacro{test-results-bl-model2-lc7-num-failrate}{41.45}

@@

\DefMacro{test-results-bl-model2-lc3-num-fail}{734}
\DefMacro{test-results-bl-model2-lc3-num-failrate}{10.82}

@@

\DefMacro{test-results-bl-model2-lc4-num-fail}{2,450}
\DefMacro{test-results-bl-model2-lc4-num-failrate}{98.16}

@@

\DefMacro{test-results-bl-model2-lc6-num-fail}{865}
\DefMacro{test-results-bl-model2-lc6-num-failrate}{86.50}

@@

\DefMacro{test-results-bl-model2-lc5-num-fail}{2,124}
\DefMacro{test-results-bl-model2-lc5-num-failrate}{100.00}

@@

\DefMacro{test-results-bl-model2-lc9-num-fail}{6,440}
\DefMacro{test-results-bl-model2-lc9-num-failrate}{84.25}

@@

\DefMacro{test-results-bl-model2-lc2-num-fail}{2,532}
\DefMacro{test-results-bl-model2-lc2-num-failrate}{31.65}

@@

\DefMacro{test-results-bl-model2-lc0-num-fail}{1,661}
\DefMacro{test-results-bl-model2-lc0-num-failrate}{96.79}

@@

\DefMacro{test-results-bl-model2-lc1-num-fail}{125}
\DefMacro{test-results-bl-model2-lc1-num-failrate}{1.44}

@@

\DefMacro{test-results-bl-model2-lc8-num-fail}{52}
\DefMacro{test-results-bl-model2-lc8-num-failrate}{0.68}
